Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-02-01 PAPER.tex
added comment
-Re-ran sigloss for PS plots -Pout = p_x syntax for eq 14&20

\begin{equation}
P_{\rm out} = P_{\rm eor} \label{eqn:anzatz},
\end{equation}
and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:

@@

Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | 
\phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$. Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out}$ is a good estimate of the injected EoR power $P_{\rm eor}$, we can write

\begin{equation}
\label{eq:Bayes}
p(P_{\rm eor} | \phat_{x}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=P_{\rm x}}
  p(\phat_{x}) ,
\end{equation}

\noindent where $p(\phat_x)$ is the probability of the measured value (given our error) and $\mathcal{L} $ is the likelihood function defined 
as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$, evaluated at the data level $\phat_x$.  We construct this distribution  
by fixing $P_{\rm in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal 
consistent with this power spectrum. The resulting distribution is normalized such that the sum is unity, and the 
whole process can then be repeated for a different value of $P_{\rm in}$.

>>>>

\begin{equation}
P_{\rm out} = \widehat{\textbf{p}}_{x} \label{eqn:anzatz},
\end{equation}
and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing} Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:

@@

Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | 
\phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$. Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out}$ is a good estimate of $\p_{x}$, we can write

\begin{equation}
\label{eq:Bayes}
p(P_{\rm in} | P_{\rm out}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=P_{\rm x}}
  p(P_{\rm out}) ,
\end{equation}

\noindent where $p(P_{\rm out})$ is the probability of the measured value (given our error) and $\mathcal{L} $ is the likelihood function defined 
as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$, evaluated at the data level $\phat_x$.  We construct this distribution  
by fixing $P_{\rm in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal 
consistent with this power spectrum. The resulting distribution is normalized such that the sum is unity, and the 
whole process can then be repeated for a different value of $P_{\rm in}$.
